### 2022-05-17 README.Rmd
update README

<!-- Document structure provided by rrtools package

@@

> Bartholdy, B. P. & Henry, A. G. (2021). _`r Title`_. bioRxiv <https://doi.org/xxx/xxx>

Our pre-print is online here:

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-->
## Contents

>>>>

<!-- Document structure provided by rrtools package -->

@@

>  _`r Title`_.
Bjørn Peare Bartholdy, Amanda G. Henry,
bioRxiv 2021.10.27.466104; doi: <https://doi.org/10.1101/2021.10.27.466104>

<!--
Our pre-print is online here:

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

## Contents
